% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

\documentclass[a4paper,12pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.90}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
% \addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
% \addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
% \newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\resheading}[1]{{\large {\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.3in}{l@{\extracolsep{\fill}}r}
		
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\

\end{tabular*}\vspace{-6pt}}

\newcommand{\projectsubheading}[2]{
\begin{tabular*}{6.3in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{#2} \\
		% \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------
\begin{document}

\begin{tabular*}{6.7in}{l@{\extracolsep{\fill}}r}
\textbf{\large GONG Li}  & +65 86206648 \\
\#02-326, 2 Dover Road &  wihoho@gmail.com\\
Singapore 130002 & https://github.com/wihoho\\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Working Experience}
\begin{itemize}
\item
	\ressubheading{WORKS APPLICATIONS}{Singapore}{Software Engineer}{Oct 2014 - Present}
	\begin{itemize}
		\resitem {Building the machine learning platform to resolve challenging problems using classification algorithms like SVM, KNN and etc. Achieved flight information extraction using SVM in 5 milliseconds, which is 40 times faster than the original rule and history based approach.}
		\resitem {Developed the core parts of a web application for managing files in 20 days, which include file system, sharing, downloading and previewing functions. Awarded the golden reel for this excellent achievement.}
		\resitem {Implemented globalization features at framework level for new products, which significantly reduced the time cost for application developers to deal with timezone and locale.}
	\end{itemize}

\item
	\ressubheading{IBM}{Singapore}{Summer Research Intern}{May 2013 - July 2013}
	\begin{itemize}
		\resitem {Implemented and compared various algorithms to perform summarization tasks with the best approach achieving 0.78 precision.} 
		\resitem {Mined useful business insights from tweets and data of enterprise social network.}
	\end{itemize}
\end{itemize}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{Nanyang Technological University}{Singapore}{B.Eng (Hons) in Computer Engineering with Minor in Business}{Sep 2010 - May 2014}
	\begin{itemize}
		\resitem {Awarded \textbf{first class honours degree} with GPA \textbf{4.67}/5.0}
		\resitem {Listed on Dean's List for Academic Year 2013-2014}
	\end{itemize}
\end{itemize} 

\resheading {School Projects}
\begin{itemize}
\item
	\projectsubheading {Final Year Project, Visual Event Recognition in Videos}{Feb 2013 - Dec 2013}
	\begin{itemize}
		\resitem {Researched and implemented a framework to recognize different images and videos by employing \textbf{cutting-edge} Transfer Learning approaches.}
		\resitem {Improved the mean average precision by 2\% through the introduction of distance calculation using Gaussian Mixture Model, which outperformed the best result reported in the original paper.}

	\end{itemize}

\item
	\projectsubheading {CPE433 Machine Learning, Face Recognition Project}{Mar 2013}
	\begin{itemize}
		\resitem {Developed a face recognition system in 3 different algorithms including eigenfaces, fishfaces and laplacianfaces, which outperformed most of the other systems.}
		\resitem {\textbf{Led} a group of three to achieve this project with high quality in only 20 days}
	\end{itemize}
\end{itemize}

\resheading{Skills}
\begin{description}
\item{\bf Technique Skills: }Java, Python, Javascript, C, C++, SQL, OOP, UML, Design Patterns

\item{\bf Languages: }Fluent in written and spoken English and Chinese
\end{description}
\end{document}